R Notebook

### 2023-11-17 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
update fitbit

## Pr-teaching phase

```{r}
main %>% 
  filter(time_span == "preparation") %>% 
  group_by(ID) %>% 
  transmute(heart_rate_m = mean(heart_rate_std),
            confidence_factor_m = mean(confidence_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            teaching_experience = teaching_experience,
            gender = gender
  ) %>%
  distinct() %>% 
  ungroup() %>% 
  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
         # gender = if_else(gender == "male",
         #                   true = 0,
         #                   false = 1),
          teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
         ) -> cor_pre

@@

## Teaching phase

```{r}
main %>% 
  filter(time_span == "teaching") %>% 
  group_by(ID) %>% 
  transmute(heart_rate_m = mean(heart_rate_std),
            confidence_factor_m = mean(confidence_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            teaching_experience = teaching_experience,
            gender = gender
  ) %>%
  distinct() %>% 
  ungroup() %>% 
  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
         gender = if_else(gender == "male",
                           true = 0,
                           false = 1),
          teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
         ) %>%
  pcor()  -> pcor_teaching

@@

## Post-teaching phase

```{r}
main %>% 
  filter(time_span == "post") %>% 
  group_by(ID) %>% 
  transmute(heart_rate_m = mean(heart_rate_std),
            confidence_factor_m = mean(confidence_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            teaching_experience = teaching_experience,
            gender = gender
  ) %>%
  distinct() %>% 
  ungroup() %>% 
  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
         gender = if_else(gender == "male",
                           true = 0,
                           false = 1),
          teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
         ) %>%
  pcor()  -> pcor_post

@@

## Interview phase

```{r}
main %>% 
  filter(time_span == "interview") %>% 
  group_by(ID) %>% 
  transmute(heart_rate_m = mean(heart_rate_std),
            confidence_factor_m = mean(confidence_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            teaching_experience = teaching_experience,
            gender = gender
  ) %>%
  distinct() %>% 
  ungroup() %>% 
  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
         gender = if_else(gender == "male",
                           true = 0,
                           false = 1),
          teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
         ) %>%
  pcor()  -> pcor_interview

@@

## End phase

```{r}
main %>% 
  filter(time_span == "end") %>% 
  group_by(ID) %>% 
  transmute(heart_rate_m = mean(heart_rate_std),
            confidence_factor_m = mean(confidence_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            teaching_experience = teaching_experience,
            gender = gender
  ) %>%
  distinct() %>% 
  ungroup() %>% 
  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
         gender = if_else(gender == "male",
                           true = 0,
                           false = 1),
          teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
         ) %>%
  pcor()  -> pcor_end

@@

@@

```{r}
df_multi <- 
  main %>% 
  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarize(disruption = mean(disruption_factor, na.rm = T),
            confidence = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  mutate(id = as.character(ID)) %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id") %>% 
  mutate(slope = abs(slope))
  # mutate(posneg = if_else(condition = slope < 0,
  #                         true = "negative",
  #                         false = "positive"))

@@

# Plot

```{r}
df_heart_rate <- 
  main %>% 
  mutate(time = time / 60) %>% 
  filter(time_span == "overall") %>%
  dplyr::select("ID","time","heart_rate") %>% 
  distinct() %>% 
  mutate(type = "a. Heart Rate (in beats per minute)")

@@

```{r}

@@

# Pre Teaching Phase

```{r echo = FALSE, results='asis'}
df_multi <- 
  main %>% 
  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarize(disruption = mean(disruption_factor, na.rm = T),
            confidence = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  mutate(id = as.character(ID)) %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id") %>%
  # mutate(posneg = if_else(condition = slope < 0,
  #                         true = "negative",
  #                         false = "positive"))

fit_pre_1 <-
  df_multi %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ disruption * posneg)

@@

fit_pre_2 <-
  df_multi %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ confidence:posneg)

@@

fit_pre_3 <-
  df_multi %>% 
  mutate(teaching_experience = log(teaching_experience + 1)) %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ teaching_experience:posneg)

@@

fit_pre_4 <-
  df_multi %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ confidence:posneg + disruption:posneg)

@@

fit_pre_5 <-
  df_multi %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ posneg:confidence + posneg:disruption + posneg:teaching_experience)

summary(fit_pre_5)

>>>>

## Pr-teaching phase
```{r}
  main %>% 
  filter(time_span == "preparation") %>% 
  group_by(ID) %>% 
  transmute(heart_rate_m = mean(heart_rate_std),
            confidence_factor_m = mean(confidence_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            teaching_experience = teaching_experience,
            gender = gender
  ) %>%
  distinct() %>% 
  ungroup() %>% 
  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
         # gender = if_else(gender == "male",
         #                   true = 0,
         #                   false = 1),
          teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
         ) -> cor_pre

@@

## Teaching phase
```{r}
main %>% 
  filter(time_span == "teaching") %>% 
  group_by(ID) %>% 
  transmute(heart_rate_m = mean(heart_rate_std),
            confidence_factor_m = mean(confidence_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            teaching_experience = teaching_experience,
            gender = gender
  ) %>%
  distinct() %>% 
  ungroup() %>% 
  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
         gender = if_else(gender == "male",
                           true = 0,
                           false = 1),
          teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
         ) %>%
  pcor()  -> pcor_teaching

@@

## Post-teaching phase
```{r}
main %>% 
  filter(time_span == "post") %>% 
  group_by(ID) %>% 
  transmute(heart_rate_m = mean(heart_rate_std),
            confidence_factor_m = mean(confidence_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            teaching_experience = teaching_experience,
            gender = gender
  ) %>%
  distinct() %>% 
  ungroup() %>% 
  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
         gender = if_else(gender == "male",
                           true = 0,
                           false = 1),
          teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
         ) %>%
  pcor()  -> pcor_post

@@

## Interview phase
```{r}
main %>% 
  filter(time_span == "interview") %>% 
  group_by(ID) %>% 
  transmute(heart_rate_m = mean(heart_rate_std),
            confidence_factor_m = mean(confidence_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            teaching_experience = teaching_experience,
            gender = gender
  ) %>%
  distinct() %>% 
  ungroup() %>% 
  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
         gender = if_else(gender == "male",
                           true = 0,
                           false = 1),
          teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
         ) %>%
  pcor()  -> pcor_interview

@@

## End phase
```{r}
main %>% 
  filter(time_span == "end") %>% 
  group_by(ID) %>% 
  transmute(heart_rate_m = mean(heart_rate_std),
            confidence_factor_m = mean(confidence_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            teaching_experience = teaching_experience,
            gender = gender
  ) %>%
  distinct() %>% 
  ungroup() %>% 
  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
         gender = if_else(gender == "male",
                           true = 0,
                           false = 1),
          teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
         ) %>%
  pcor()  -> pcor_end

@@

summary(regr_teaching1)
summary(regr_teaching2)
summary(regr_teaching3)
summary(regr_teaching4)

@@

# Multiple Linear Regression (Slope)
```{r}

  main %>% 
  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  # summarize(disruption_factor = mean(disruption_factor, na.rm = T),
  #           confidence_factor = mean(confidence_factor, na.rm = T),
  #           teaching_experience) %>% 
  transmute(id = as.character(ID),
            disruption_factor = mean(disruption_factor, na.rm = T),
            confidence_factor = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id") -> data_regression_slope

for (i in unique(data_regression_slope$Phase)) {

  cache <- data_regression_slope %>% 
    filter(Phase == i)

  regr1 <-
    lm(slope ~ teaching_experience,
    data = cache)

@@

# Overall Plot (unstd./std.)
```{r}
df_heart_rate <- 
  main %>% 
  mutate(time = time / 60) %>% 
  filter(time_span == "overall") %>%
  dplyr::select("ID","time","heart_rate") %>% 
  distinct() %>% 
  mutate(type = "a. Heart Rate (in beats per minute)")

@@

# Mean Plot
```{r}

@@

# Pre Teaching Phase
```{r echo = FALSE, results='asis'}
df_multi <- 
  main %>% 
  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarize(disruption_factor = mean(disruption_factor, na.rm = T),
            confidence_factor = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  mutate(id = as.character(ID)) %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id")
  # mutate(posneg = if_else(condition = slope < 0,
  #                         true = "negative",
  #                         false = "positive"))

fit_pre_1 <-
  df_multi %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ teaching_experience)

@@

fit_pre_2 <-
  df_multi %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ teaching_experience + disruption_factor)

@@

summary(fit_pre_1)$r.squared - summary(fit_pre_2)$r.squared

fit_pre_3 <-
  df_multi %>% 
  mutate(teaching_experience = log(teaching_experience + 1)) %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ teaching_experience + confidence_factor)

@@

summary(fit_pre_1)$r.squared - summary(fit_pre_2)$r.squared - summary(fit_pre_3)$r.squared

fit_pre_4 <-
  df_multi %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ teaching_experience + confidence + disruption)

@@
